---
title: "In Class Exercises - Sorting and Filtering"
author: "Sarina Oshiro"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    self-contained: true
    toc: true
    toc-location: left
---

## Setup and Loading Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load the packages we'll need
# Remember, think of this like packing for our trip
# (We don't take the whole closet, only what we need)
library(tidyverse)
library(lubridate)

```

Run this line below load the data for this assignment. It will load a dataframe called "impeach," containing U.S. House Democrats and whether they supported the first impeachment of Pres. Trump, along with when they announced such support.

```{r}

impeach <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRh8d5JaDqBtByzNw2JZF3idaACobDhhk-p7chJoktA0HawELHFOvjQOqCpzGA4MGONvPlR7GASqW-K/pub?gid=1765341510&single=true&output=csv")


```

Let's see what we have:

```{r}

impeach


```

## Exercise Questions

*For the questions below, write your R code to return the requested records in the code chunk provided.*

1)  The column "for_impeachment" indicates whether the member has publicly called for an impeachment inquiry. Filter to return only the ones where the answer is NO.

## I am filtering for the impeach dataset AND a "NO" response in the for_impeachment column.

```{r}

filter(impeach, for_impeachment == "NO")



```

2)  Filter to return only results where a member is both against impeachment, and comes from a district that President Trump won in 2016 (which is noted in the "p16winningparty" column).
-
-
## Filtering again for impeach dataset, NO response in for_impeachment column, AND an "R" response in the p16winningparty column (which represents districts with Trump, the Republican, won in 2016)
```{r}


filter(impeach, for_impeachment == "NO", p16winningparty == "R" )



```

3)  Filter for only results where a member is against impeachment, comes from a district that President Trump won in 2016 (which is noted in the "p16winningparty" column), and also comes from a district that Mitt Romney won in 2012 ("p12winningparty").
-
-
## Filtering for impeach dataset, "NO" response in the for_impeachment column, an "R" response in the p16winningparty column, AND an "R" response in the 2012 column (which represents districts where the Republican, Mitt Romney, won the presidential race)
```{r}


filter(impeach, for_impeachment == "NO", p16winningparty == "R", p12winningparty == "R")



```

4)  Filter for only results from September 2019 where a member is a YES for impeachment.
-
-
## I am filtering for impeach dataset, responses of "2019" in the column for years, AND a "YES" response in the column for_impeachment. 
```{r}


filter(impeach, date_month == "9", date_year == "2019", for_impeachment == "YES")


```

5)  Filter for only results where a member is a YES for impeachment and is from a district where Clinton won more than 70 percent of the vote in 2016 (found in column "clinton_percent").
-
-
## Filtering for the impeach dataset, a "YES" vote in the for_impeachment column, and rows where the number in the clinton_percent column was greater than (>) 70. 
```{r}

filter(impeach, for_impeachment == "YES", clinton_percent > 70)



```

6)  Sort the entire dataframe based on the percentage of a district that has a bachelor's degree or higher ("pct_bachelors"), from lowest to highest.
-
-
## To sort, I indicated the dataframe and then used the arrange function, which sorts the data by the column I indicated (pct_bachelors) from lowest to highest by default. 

```{r}


impeach %>% 
  arrange(pct_bachelors)
  



```

7)  Sort the just those who are NO on impeachment based on the percentage of a district that has a bachelor's degree or higher ("pct_bachelors"), from lowest to highest.
-
-
## Filtering for impeach dataset, then "NO" vote in the for_impeachement column, and then I sorted it using the arrange function on the pct_bachelors column. Again, it sorts in the direction of  lowest to highest by default. 
```{r}

filter(impeach, for_impeachment == "NO") %>%
   arrange(pct_bachelors)


```

8)  Sort the just those who are NO on impeachment based on the percentage of a district that has a bachelor's degree or higher ("pct_bachelors"), from lowest to highest.

Then filter those records by only those whose bachelor's percentage is below the national average (found in the "pct_bachelors_compared_to_national" column).
-
-
## Filtering for impeach dataset, then "NO" response in for_impeachment column, then "BELOW" response in the pct_bachelors_compared_to_national column. I sorted this filtered data using the arrange feature last, in order to keep the filter commands together. 
```{r}

filter(impeach, for_impeachment == "NO", pct_bachelors_compared_to_national == "BELOW") %>%
   arrange(pct_bachelors)


```

9)  Filter for only members from New Jersey who are NO on impeachment.
-
-
## Filter by the impeach dataset, then responses of "NJ" under state (for New Jersey), then a "NO" response in the for_impeachment column. 
```{r}


filter(impeach, state == "NJ", for_impeachment == "NO")


```

10) Filter for those who were YES on impeachment, with a declared date prior to 2019. So only those with dates before 2019. Then sort those so that the highest Clinton vote percentages are at the top.
-
-
## Filter by the impeach dataset, then "YES" responses for the for_impeachment column, then responses of less than (>) "2019" in the date_year column, and then I arranged all of those responses in descending order (highest to lowest) based on responses in the clinton_percent column.
```{r}


filter(impeach, for_impeachment == "YES", date_year < "2019") %>%
  arrange(desc(clinton_percent))


```
